Trends of SDR in Thessaloniki

### 2023-09-18 Article.Rmd
Commit 2023-09-18 19:11

```{r echo=F, include=T, warning=FALSE, message=FALSE}
suppressMessages(
    res <- rmarkdown::find_pandoc(dir = '/usr/lib/rstudio/resources/app/bin/quarto/bin/tools')
)
## document configurations 
knitr::opts_chunk$set(comment    = ""      )
# knitr::opts_chunk$set(dev        = "pdf"   )
knitr::opts_chunk$set(out.width  = "70%"   )
knitr::opts_chunk$set(fig.align  = "center")
knitr::opts_chunk$set(fig.pos    = 'h!'    )
options(knitr.graphics.auto_pdf = FALSE)
library(pander)
library(data.table)
## load data from trends analysis
load("./data/common_data_14_2.Rda")
## number of measurements for each dataset
SDR_N_All   <- sum(  ALL_1_daily_DESEAS[,GLB_att_N])
SDR_N_Clear <- sum(CLEAR_1_daily_DESEAS[,GLB_att_N])
SDR_N_Cloud <- sum(CLOUD_1_daily_DESEAS[,GLB_att_N])
## TSI data span info
TSIinfo <- data.table(read.csv("./figures/tbl_tsi_info.dat",
                    strip.white = TRUE,
                    sep = ";",
                    header = TRUE))
## variables we use in the analysis
source("./DHI_GHI_0_variables.R")

@@

<!-- \footnotesize -->
```{r trendtable, echo=F}
panderOptions("table.alignment.default", "center")
pander(LT,
       caption = paste0("\\label{tab:trendtable}Trends of daily SDR means, for different sky conditions for ", year(min(ALL_1_daily_DESEAS$Date)), " - ", year(max(ALL_1_daily_DESEAS$Date)), ". For all cases the statistical significance is above $", LTminSSig, "\\,\\%$."))
```
<!-- \normalsize -->

@@

<!-- \footnotesize -->
```{r trendseasontable, echo=F}
## arrange columns
spp <- spp[,c(
      "Sky condition",
      "Season",
      "Trend [%/year]", 
      # "Trend p-value", 
      "Statistical signif. [%]"
      )]

rownames(spp) <- NULL
# panderOptions("table.alignment.default", "left")
panderOptions("table.alignment.default", "center")
pander(spp,
       justify = c('center', 'right', 'right', 'center'),
       split.table = Inf,
       caption = "\\label{tab:trendseasontable}SDR linear trends of monthly anomalies for each season of the year.")
```
<!-- \normalsize -->

>>>>

```{r echo=F, include=T, warning=FALSE, message=FALSE}
suppressMessages(
    res <- rmarkdown::find_pandoc(dir = '/usr/lib/rstudio/resources/app/bin/quarto/bin/tools')
)
## document configurations 
knitr::opts_chunk$set(comment    = ""      )
# knitr::opts_chunk$set(dev        = "pdf"   )
knitr::opts_chunk$set(out.width  = "70%"   )
knitr::opts_chunk$set(fig.align  = "center")
knitr::opts_chunk$set(fig.pos    = 'h!'    )
options(knitr.graphics.auto_pdf = FALSE)
library(pander)
library(data.table)
library(kableExtra)
## load data from trends analysis
load("./data/common_data_14_2.Rda")
## number of measurements for each dataset
SDR_N_All   <- sum(  ALL_1_daily_DESEAS[,GLB_att_N])
SDR_N_Clear <- sum(CLEAR_1_daily_DESEAS[,GLB_att_N])
SDR_N_Cloud <- sum(CLOUD_1_daily_DESEAS[,GLB_att_N])
## TSI data span info
TSIinfo <- data.table(read.csv("./figures/tbl_tsi_info.dat",
                    strip.white = TRUE,
                    sep = ";",
                    header = TRUE))
## variables we use in the analysis
source("./DHI_GHI_0_variables.R")

@@

<!-- \footnotesize -->
```{r trendtable, echo=F}
panderOptions("table.alignment.default", "center")
pander(LT,
       caption = paste0("\\label{tab:trendtable}Trends of daily SDR means, for different sky conditions for ", year(min(ALL_1_daily_DESEAS$Date)), " - ", year(max(ALL_1_daily_DESEAS$Date)), ". For all cases the statistical significance is above $", LTminSSig, "\\,\\%$."))

x_latex <- knitr::kable(LT,
                        format   = "latex",
                        booktabs = T,
                        escape   = T,
                        # format.args = list(digits = 3),
                        linesep  = "",
                        # align    = "ccrr",
                        caption  = "sssssss")
x_latex %>%
    collapse_rows(columns = 1, valign = "middle", latex_hline = "custom") %>%
    kable_styling(latex_options = c("striped",
                                    "hold_position")
                  )

```
<!-- \normalsize -->

@@

<!-- \footnotesize -->

```{r trendseasontable, echo=F}
## arrange columns
spp <- spp[,c(
      "Sky condition",
      "Season",
      "Trend [%/year]", 
      # "Trend p-value", 
      "Statistical signif. [%]"
      )]

rownames(spp) <- NULL
# panderOptions("table.alignment.default", "left")
# panderOptions("table.alignment.default", "center")
# pander(spp,
#        justify = c('center', 'right', 'right', 'center'),
#        split.table = Inf,
#        caption = "\\label{tab:trendseasontable}SDR linear trends of monthly anomalies for each season of the year.")

## use kable

x_latex <- knitr::kable(spp,
                        format   = "latex",
                        booktabs = T,
                        escape   = T,
                        # format.args = list(digits = 3),
                        linesep  = "",
                        align    = "ccrr",
                        caption  = "\\label{tab:trendseasontable}SDR linear trends of monthly anomalies for each season of the year.")
x_latex %>%
    collapse_rows(columns = 1, valign = "middle", latex_hline = "custom") %>%
    kable_styling(latex_options = c("striped",
                                    "hold_position")
                  ) 
# position = "float_left"

```

<!-- \normalsize -->
